\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-07-18 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex

% !TEX encoding = IsoLatin
%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[oneside,english]{book}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{babel}
\usepackage{float}
\usepackage{textcomp}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[authoryear]{natbib}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},backref=section,colorlinks=false,pdfpagemode=None]
 {hyperref}
\hypersetup{
 pdftex,pdfstartview=FitH,pdfpagelayout=SinglePage}
\usepackage{breakurl}

@@

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team:
in alphabetical order,
Jean-Paul (Pablo) Ampuero,
Kangchen Bai,
Piero Basini,
Céline Blitz,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Percy Galvez,
Dominik Göddeke,
Vala Hjörleifsdóttir,
Sue Kientz,
Dimitri Komatitsch,
Jesús Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
René Matzen,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer,
David Michéa,
Surendra Nadh Somala,
Tarje Nissen-Meyer,
Daniel Peter,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Jean-Pierre Vilotte,
Zhinan Xie,
Hejun Zhu.\\

@@

The SCOTCH library \citep{PeRo96} provides efficent static mapping,
graph and mesh partitioning routines. SCOTCH is a free software package
developed by François Pellegrini et al. from LaBRI and INRIA in Bordeaux,
France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}.
In case no SCOTCH libraries can be found on the system, the configuration
will bundle the version provided with the source code for compilation.
The path to an existing SCOTCH installation can to be set explicitly
with the option \texttt{-{}-with-scotch-dir}. Just as an example:
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90~-{}-with-scotch-dir=/opt/scotch
\end{lyxcode}
If you use the Intel ifort compiler to compile the code, we recommend
that you use the Intel icc C compiler to compile Scotch, i.e., use:
\begin{lyxcode}
./configure~CC=icc~FC=ifort~MPIFC=mpif90
\end{lyxcode}

@@

\noindent To compile the code on an IBM BlueGene, Laurent Léger from
IDRIS, France, suggests the following: compile the code with

@@

An efficient partitioning is important because it leverages the overall
running time of the application. It amounts to balance the number
of elements in each slice while minimizing the communication costs
resulting from the placement of adjacent elements on different processors.
\texttt{decompose\_mesh} depends on the SCOTCH library \citep{PeRo96},
which provides efficent static mapping, graph and mesh partitioning
routines. SCOTCH is a free software package developed by François
Pellegrini et al. from LaBRI and INRIA in Bordeaux, France, downloadable
from the web page \url{https://gforge.inria.fr/projects/scotch/}.
\\

>>>>

% !TEX encoding = IsoLatin
%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[oneside,english]{book}
\usepackage[T1]{fontenc}
%% DK DK we do not accept accented letters, use the old LaTeX syntax
%% DK DK for them instead: \'e \`e  \"e \^e and so on.
%% DK DK \usepackage[latin1]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{babel}
\usepackage{float}
\usepackage{textcomp}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[authoryear]{natbib}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},backref=section,colorlinks=false,pdfpagemode=None]
 {hyperref}
\hypersetup{
 pdftex,pdfstartview=FitH,pdfpagelayout=SinglePage}
\usepackage{breakurl}

@@

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team:
in alphabetical order,
Jean-Paul (Pablo) Ampuero,
Kangchen Bai,
Piero Basini,
C\'eline Blitz,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Percy Galvez,
Dominik Göddeke,
Vala Hjörleifsdóttir,
Sue Kientz,
Dimitri Komatitsch,
Jesús Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Ren\'e Matzen,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer,
David Mich\'ea,
Surendra Nadh Somala,
Tarje Nissen-Meyer,
Daniel Peter,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Jean-Pierre Vilotte,
Zhinan Xie,
Hejun Zhu.\\

@@

The SCOTCH library \citep{PeRo96} provides efficent static mapping,
graph and mesh partitioning routines. SCOTCH is a free software package
developed by Fran\c{c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux,
France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}.
In case no SCOTCH libraries can be found on the system, the configuration
will bundle the version provided with the source code for compilation.
The path to an existing SCOTCH installation can to be set explicitly
with the option \texttt{-{}-with-scotch-dir}. Just as an example:
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90~-{}-with-scotch-dir=/opt/scotch
\end{lyxcode}
If you use the Intel ifort compiler to compile the code, we recommend
that you use the Intel icc C compiler to compile Scotch, i.e., use:
\begin{lyxcode}
./configure~CC=icc~FC=ifort~MPIFC=mpif90
\end{lyxcode}

@@

\noindent To compile the code on an IBM BlueGene, Laurent L\'eger from
IDRIS, France, suggests the following: compile the code with

@@

An efficient partitioning is important because it leverages the overall
running time of the application. It amounts to balance the number
of elements in each slice while minimizing the communication costs
resulting from the placement of adjacent elements on different processors.
\texttt{decompose\_mesh} depends on the SCOTCH library \citep{PeRo96},
which provides efficent static mapping, graph and mesh partitioning
routines. SCOTCH is a free software package developed by Fran\c{c}ois
Pellegrini et al. from LaBRI and INRIA in Bordeaux, France, downloadable
from the web page \url{https://gforge.inria.fr/projects/scotch/}.
\\
